\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-08 popl-2019-journal-v/proving-full-abstraction.tex
[POPLjv] Add Iris remark in solving recursive domain equation section

>>>>

Recursive domain equations are so common and the solution so standard that frameworks implement them lifting the technical burden of constructing the world by hand.
The technique we use to solve our recursive domain equation is essentially the same used internally in the program logic framework Iris~\citep{iris1,iris2,iris3} to construct worlds.
We believe the worlds presented here could be developed in Iris.
Had we done the development in Iris Coq, then we would have had the world tool support of Iris and the rigorousness of Coq which, in hindsight, would have been very beneficial.
